学術論文

### 2025-07-05 articles.Rmd
update

- [51] Buchanan, E. M.,...Kunisato, Y.,...Suchow, J. (in press). Measuring the Semantic Priming Effect Across Many Languages. Nature Human Behaviour.

>>>>

- [53] Soda, T., Toyama, A., Takeda1, M., Kunisato, Y.,  & Yamashita, Y. (in press). Reliability and Validity of the DSM-5 Level 1 Cross-Cutting Symptom Measure in Japan: Insights into General and Specific Psychiatric Symptom Assessment.

- [52] Kowal, M.,...Kunisato, Y.,...Prazeres, F. (in press). Cross-cultural data on romantic love and mate preferences from 117,293 participants across 175 countries. Scientific Data.

- [51] Buchanan, E. M.,...Kunisato, Y.,...Lewis, S.C. (in press). Measuring the semantic priming effect across many languages. Nature Human Behaviour.
